Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-24 poster/main.tex
Switch to 3 column layout

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

Linear RNNs and convolutional models such as strongly typed RNNs, Wavenet, Bytenet,
quasi-RNNs, and simple recurrent units
have achieved state of the art results on many sequential tasks with rapid training times.

@@

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

@@

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

\begin{block}{Scan diagram and complexity??}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

%----------------------------------------------------------------------------------------
%	IMPORTANT RESULT
%----------------------------------------------------------------------------------------

\begin{alertblock}{Important Result (???)}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit.

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

@@

\begin{table}[t]
  \vspace{2ex}
  \caption{Parallel kernel speedup for a variety of LS-RNNs.}
\begin{center}
\begin{tabular}{lrrrr}
\label{table:rnn-throughput}
\small{Seq.\ Len.} & \small{SRU} & \small{QRNN(2)}
  & \small{QRNN(10)} & \small{GILR-LSTM}\\ \midrule
16 & 0.28 & 0.38 & 0.78 & 0.61\\
256 & 0.84 & 0.86 & 0.99 & 0.91\\
4,096 & 1.38 & 1.18 & 1.05 & 0.98\\
65,536 & 9.21 & 6.68 & 2.05 & 1.41\\ \bottomrule
\end{tabular}
\end{center}
\end{table}
\end{block}

@@

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

@@

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2

\end{column} % End of the second column

>>>>

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.30\paperwidth} % Width of one column
\setlength{\twocolwid}{0.624\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

Linear RNNs and convolutional models such as strongly typed RNNs, Wavenet, Bytenet,
Quasi-RNNs, and simple recurrent units
have achieved state of the art results on many sequential tasks with rapid training times.

@@

\begin{column}{\onecolwid} % Begin a column which is two columns wide (column 2)

@@

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrr}
\label{table:rnn-throughput}
\small{Seq.\ Len.} & \small{SRU} & \small{QRNN(2)}
  & \small{QRNN(10)} & \small{GILR-LSTM}\\ \midrule
16 & 0.28 & 0.38 & 0.78 & 0.61\\
256 & 0.84 & 0.86 & 0.99 & 0.91\\
4,096 & 1.38 & 1.18 & 1.05 & 0.98\\
65,536 & 9.21 & 6.68 & 2.05 & 1.41\\ \bottomrule
\end{tabular}
\end{center}
\vspace{2ex}
\caption{Parallel kernel speedup for a variety of LS-RNNs.}
\end{table}
\end{block}

@@

@@
